Bug Insertion

### 2015-07-14 Bug_Insertion.tex
Modifying figures

[I have another graph where the responsibility in 'More than one commit' depend on the degree of responsibility of each commit inside a ticket
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{prueba}
\end{figure}
]

>>>>

[Another graph  figure~\ref{fig:degree}  shows the responsibility in 'More than one commit' depend on the degree of responsibility of each commit inside a ticket
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{prueba} 
\caption{Degree of responsibility in more than one commit} \label{fig:degree}
\end{figure}
]
